```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Checking the Installed Version of Gitbook

Gitbook.io is under active development. The `gitbookInfo` function will indicate whether a new version of Gitbook is available.

```{r gitbookInfo}
gitbookInfo()
```

If a new version is available, the `installGitbook` function will install the latest version.

```{r installgitbook, eval=FALSE}
installGitbook()
```

Additionally, the `checkForGitbook` function will also indicate whether Gitbook is installed and available but will not check the [Node Package Modules](https://www.npmjs.org/) website for the currently available version.

```{r checkForGitbook}
checkForGitbook()
```

The `quiet` parameter will not print any messages. The function returns a logical indicating whether Gitbook is available or not. This may be useful if you are automating your Gitbook development.

```{r checkForGitbookQuiet}
isAvailable <- checkForGitbook(quiet=TRUE)
isAvailable
```

