```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Installation

The `gitbook` R package is currently avaiable on [Github](http://github.com). The `devtools` `r citep(bib['devtools'])` package provides a function to install R packages directly from github.

```{r installPackage, eval=FALSE}
devtools::install_github('jbryer/Rgitbook')
```

The [Gitbook.io](http://gitbook.io) framework is built using [Node.js](http://nodejs.org/). Installers are available for most major platforms and can be downloaded from the Node.js website at [http://nodejs.org/download/](http://nodejs.org/download/).

Once Node.js is installed the `installGitbook` function will attempt to download and install the Gitbook.io framework.

```{r installGitbook, eval=FALSE}
installGitbook()
```

We can verify that Gitbook is installed using the `checkForGitbook` function.

```{r verifyinstall}
checkForGitbook()
```

### If Gitbook Installation Fails

It is possible that the installation of Gitbook will not work since it requires root/administrator access. The `installGitbook` function will print an error message to help you install outside of R. On Mac and Linux systems, the following Unix command will install Gitbook:

```
sudo npm install gitbook -g
```

If you wish to build PDF versions of your book, install the PDF format using the following command:

```
sudo npm install gitbook-pdf -g
```


