```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Building R Markdown Files

NOTE: The `buildRmd` function will be called from the `buildGitbook` function by default and therefore it is not necessary to call this function directly. However, this page will describe the process.

The first step in building a Gitbook is to convert all R Markdown files to markdown. The `buildRmd` function will locate each `.Rmd` file in your project and build it using the `knitr` package. This function will also create a `.rmdbuild` file in the root of your Gitbook website. This file contains information about the last build. In short, this allows the `buildRmd` file to only rebuild files that have changed since the last build therefore substantially decreasing the amount of time it takes to rebuild your book. 

```{r buildRmd, eval=FALSE}
buildRmd()
```

There are a number of parameters for the `buildRmd` function.

* `dir` (default is `getwd()`) - Specifies the directory containing your book source files.
* `clean` (default is `FALSE`) - If `TRUE`, all `.Rmd` files will be built even if they have not changed since the last build.
* `log.dir` - If specified, the output from the `knit` process will be saved to a log file instead of the console. A seperate log file for each `.Rmd` file will be created.
* `log.ext` (default is `.txt`) - The file extension for log files if used.
* `...` Other paramaters passed to the `knit` function.
